\subsection{Faculty Representative}
\label{sec:facultyrep}
The faculty representative is a graduate student who represents the interests of the CS Women general membership to the faculty. The faculty representative role is similar to the existing GradRep role, but is a non-voting voice. 

Although there is often at least one woman among the four voting GradReps, this individual is elected by and represents the general graduate student population. The Faculty Representative role mirrors the Faculty Liaison role.


\subsubsection{Responsibilities}
The faculty representative is expected to attend monthly faculty meetings. They will also meet with faculty and the co-chairs as the occasion arises.

\subsubsection{Eligibility}
Any general member who is a Graduate student in CICS in good standing, who has either (a) held an assistantship for two semesters or (b) completed 15 course credit hours, applied to a graduate degree may run for this position.

Unlike GradReps, the faculty representative does not need to have passed portfolio in order to serve. This is a non-voting position designed to represent the core needs of the membership to the faculty.


\subsubsection{Selection}
Faculty representatives are selected according to the following time table:
\begin{center}
\begin{tabular}{|l p{5in}|}
	\hline
	Timeframe & Action\\
	\hline
	January & Solicit nominations for faculty representatives among the CS Women membership. Self-nominations are allowed. \\
	First week of February & Withdrawal period. Anyone nominated who is not interested in the position should withdraw during this time. \\
	Late February & Nominees each provide a short paragraph introducing themselves and providing any additional information that is germane to selection. \\
	Early March & CS Women membership cast ballots for the faculty representative. Co-chairs tabulate the votes and announce the new representative.\\
	\hline
\end{tabular}
\end{center}

\subsubsection{Term Length}
Faculty representatives have term lengths of one academic year. They may serve unlimited number of terms.

\subsubsection{Approximate Time Commitment}
The approximate time commitment for the faculty representative varies. They must be available for monthly faculty meetings. However, if issues come up, they may be required to meet with the faculty about specific concerns more frequently. Expect an average of 1 hour/week time commitment.