\subsection{Scribe}
\label{sec:scribe}

\subsubsection{Responsibilities}
At least one scribe must attend every lunch. The scribe must ensure that attendance is taken and should take notes on the meeting. Immediately after the meeting, the scribe will post a summary of the lunch, along with attendance numbers, and acknowledgement of sponsorship when applicable. Scribes are also expected to help with the setup and breakdown of lunches. 

If the scribe cannot attend, they must contact the co-chairs as soon as possible and find a replacement to take notes. When there are two scribes, they may alternate responsibilities.

Scribes should also try to attend co-chair meetings and take notes when applicable.


The scribe takes notes during meetings and lunches. They may also take photographs of the speaker and/or students, with the speaker's permission.\footnote{Students who have not signed the College's photo release form should contact the co-chairs. Nearly every full-time student will have done so.} Notes from co-chair meetings should be held in a public repository. Notes from lunches should be edited into a blog post, to be posted on the publicly-facing CS Women website. 

\subsubsection{Eligibility}
Any of the general membership should become the scribe. Scribes should be chosen prior to the first meeting. Up to two members may be scribes.

\subsubsection{Selection}
We solicit the general membership for volunteers.

\subsubsection{Term Length}
Scribes serve one semester terms. There are no restrictions on the number of terms served.

\subsubsection{Approximate Time Commitment}
The average weekly time commitment is 1-2 hours. However, scribes are not expected to attend every co-chair meeting. Therefore, the bulk of the time commitment is on the day of the lunch.